---
title: "Tables and Figures"
bibliography: references.bib
biblio-style: apsr
nocite: |
  @*
format:
  pdf:
    documentclass: article
    geometry: margin=0.75in
    fig-cap-location: top
    header-includes:
      - "\\usepackage{adjustbox}"
      - "\\usepackage{threeparttable}"
      - "\\usepackage{pdflscape}"
      - "\\usepackage{longtable}"
      - "\\usepackage{array}"
      - "\\newlength{\\rotwidth}"
      - "\\AtBeginDocument{\\setlength{\\rotwidth}{\\textheight}}"
execute:
  echo: false
  message: false
  warning: false
---

```{r setup}
library(tidyverse)
library(gt)
load("../output/results.rda")

convert_to_latex <- function(gt_table) {
  gt_table %>%
    as_latex() %>%
    strsplit(split = "\n", fixed = TRUE) %>%
    unlist() %>%
    str_replace(fixed("{tabular*}"), "{tabular}") %>%
    str_replace(fixed("{\\linewidth}{@{\\extracolsep{\\fill}}"), "{")
}

convert_to_longtable <- function(gt_table) {
  lines <- gt_table %>%
    as_latex() %>%
    strsplit(split = "\n", fixed = TRUE) %>%
    unlist() %>%
    str_replace(fixed("{tabular*}"), "{longtable}") %>%
    str_replace(fixed("{\\linewidth}{@{\\extracolsep{\\fill}}"), "{")
  lines <- head(lines[-(1:2)], -1)
  first_midrule <- which(str_detect(lines, fixed("\\midrule")))[1]
  append(lines, "\\endhead", after = first_midrule)
}

wrap_cols <- function(lines, widths) {
  idx <- which(str_detect(lines, fixed("\\begin{tabular}{")))[1]
  full_spec <- str_match(lines[idx], "^\\\\begin\\{tabular\\}\\{(.*)\\}$")[1, 2]
  tokens <- str_extract_all(full_spec, "\\|?[lcr]")[[1]]
  for (pos in names(widths)) {
    i <- as.integer(pos)
    bar <- if (str_starts(tokens[i], fixed("|"))) "|" else ""
    tokens[i] <- paste0(bar, ">{\\raggedright\\arraybackslash}p{", widths[[pos]], "}")
  }
  lines[idx] <- paste0("\\begin{tabular}{", paste(tokens, collapse = ""), "}")
  lines
}

shrink <- function(gt_tbl) tab_options(gt_tbl, table.font.size = px(9))

table_block <- function(gt_tbl, title, subtitle = NULL, notes = NULL,
                         width_cmd = "\\textwidth", stretch = FALSE,
                         center = FALSE, wrap = NULL) {
  latex_lines <- convert_to_latex(gt_tbl)
  if (!is.null(wrap)) latex_lines <- wrap_cols(latex_lines, wrap)
  body <- head(latex_lines[-(1:2)], -1)
  notes_block <- if (is.null(notes)) {
    character(0)
  } else {
    c(
      "\\begin{tablenotes}[flushleft]",
      "\\footnotesize",
      "\\setlength{\\labelsep}{0pt}",
      paste0("\\item \\emph{Notes}: ", notes),
      "\\end{tablenotes}"
    )
  }
  adjustbox_opt <- if (stretch) "width" else "max width"
  table_lines <- c(
    paste0("\\begin{adjustbox}{", adjustbox_opt, "=", width_cmd, "}"),
    "\\begin{threeparttable}",
    body,
    notes_block,
    "\\end{threeparttable}",
    "\\end{adjustbox}"
  )
  if (center) {
    table_lines <- c("\\begin{center}", table_lines, "\\end{center}")
  }
  title_lines <- paste0("\\textbf{", title, "}")
  if (!is.null(subtitle)) {
    title_lines <- c(title_lines, "", subtitle)
  }
  c(
    title_lines,
    "\\vspace{4pt}",
    "",
    table_lines
  )
}

longtable_block <- function(gt_tbl, title, notes = NULL) {
  notes_lines <- if (is.null(notes)) {
    character(0)
  } else {
    c("", "\\footnotesize", paste0("\\emph{Notes}: ", notes))
  }
  c(
    paste0("\\textbf{", title, "}"),
    "\\vspace{4pt}",
    "",
    convert_to_longtable(gt_tbl),
    notes_lines
  )
}

landscape_wrap <- function(lines) c("\\begin{landscape}", lines, "\\end{landscape}")
```

{{< pagebreak >}}

```{r}
#| fig-width: 6
#| out-width: "100%"

fig_wgi_dotstrip
```

Fig. 1.—Institutional Quality (Worldwide Governance Indicators), by Country. This figure plots each sample country's estimate, as of 2024, on six World Bank Worldwide Governance Indicators. Higher values indicate stronger institutional quality; estimates range from approximately -2.5 (weak) to 2.5 (strong). Countries are grouped by region (Central Asia vs. Baltic states). All variables are defined in Appendix A.

{{< pagebreak >}}

```{r}
#| results: asis

cat(paste(landscape_wrap(table_block(
  shrink(tab_regulations_mandatory),
  title = "Table 1: ESG Disclosure Regulations by Country",
  subtitle = "Panel A: Mandatory ESG Disclosure Regulations",
  stretch = TRUE,
  width_cmd = "\\rotwidth",
  wrap = c(`2` = "1.2in", `3` = "1.3in", `6` = "1.5in", `7` = "1.3in")
)), collapse = "\n"))
```

```{r}
#| results: asis

cat(paste(landscape_wrap(table_block(
  shrink(tab_regulations_guidance),
  title = "Table 1: ESG Disclosure Regulations by Country --- continued",
  subtitle = "Panel B: Voluntary ESG Disclosure Guidance",
  notes = paste(
   "Panel A lists the mandatory ESG disclosure regulations in force in",
    "each sample country as of the data collection period (June 2026);",
    "Panel B lists non-binding ESG disclosure guidance issued in the",
    "same countries and period. N Affected is computed over the full",
    "disclosure sample (N = 141; Table 2, Panel A) and reports",
    "the number of sample firms subject to each individual regulation (Panel A) or",
    "eligible to follow the guidance (Panel B). A firm may be subject to more than one regulation. Data are hand collected",
    "from national regulatory texts and exchange rules."
  ),
  stretch = TRUE,
  width_cmd = "\\rotwidth",
  wrap = c(`2` = "1.2in", `3` = "1.3in", `6` = "1.5in", `7` = "1.3in")
)), collapse = "\n"))
```

```{r}
#| results: asis

cat(paste(landscape_wrap(table_block(
  shrink(tab_sample_selection_a),
  title = "Table 2: Sample Selection and Composition",
  subtitle = "Panel A: Full Listed Population",
  stretch = TRUE,
  width_cmd = "\\rotwidth",
  wrap = c(`1` = "2.8in")
)), collapse = "\n"))
```

```{r}
#| results: asis

cat(paste(landscape_wrap(table_block(
  shrink(tab_sample_selection_b),
  title = "Table 2: Sample Selection and Composition --- continued",
  subtitle = "Panel B: Final Regression Sample",
    notes = paste(
    "Panel A reports the sample selection procedure for all publicly",
    "listed, non-financial firms across the ten stock exchanges covered",
    "by the study, by country and region. The starting point is the full",
    "population of firms listed on each exchange collected in June 2026.", 
    "Panel A's disclosure sample is the sample",
    "used for the disclosure-coverage statistics reported in Table 3 and",
    "Figure 2. Panel B continues the selection from the disclosure sample",
    "down to the final regression sample. Exchange abbreviations",
    "are: KASE, Kazakhstan Stock Exchange; AIX, Astana International",
    "Exchange; UZSE, Republican Stock Exchange Toshkent; KSE, Kyrgyz",
    "Stock Exchange; BTS, Stock Exchange of Kyrgyzstan; AGB, Ashgabat",
    "Stock Exchange; CASE, Central Asian Stock Exchange; TLN, Nasdaq",
    "Tallinn; RIG, Nasdaq Riga; VLN, Nasdaq Vilnius. The Grand Total row in Panel B is",
    "the final sample used in the descriptive statistics, correlation,",
    "and regression analyses reported in Tables 4 through 9."
  ),
  stretch = TRUE,
  width_cmd = "\\rotwidth",
  wrap = c(`1` = "2.8in")
)), collapse = "\n"))
```

{{< pagebreak >}}

```{r}
#| results: asis

cat(paste(landscape_wrap(table_block(
  shrink(tab_disclosure_coverage),
  title = "Table 3: Disclosure Coverage by Region and Country",
  notes = paste(
    "This table reports, by country, the number of sample firms",
    "publishing each report type, drawn from the full disclosure sample (N = 141; Table 2, Panel A). ESG Disclosure is the",
    "union, not the sum, of (a) and (b): a firm with both an ESG",
    "standalone report and ESG information in its integrated annual",
    "report is counted once under ESG Disclosure but appears in both",
    "(a) and (b). Row (c) reports the number of such firms, by country",
    "and in total. All variables are defined in Appendix A."
  ),
  stretch = TRUE,
  width_cmd = "\\rotwidth",
  wrap = c(`1` = "2.4in")
)), collapse = "\n"))
```

```{r}
#| results: asis

cat(paste(table_block(
  shrink(tab_desc_panel_a),
  title = "Table 4: Descriptive Statistics by Region",
  subtitle = "Panel A: Binary Variables"
), collapse = "\n"))
```

```{r}
#| results: asis

cat(paste(table_block(
  shrink(tab_desc_panel_b),
  title = "Panel B: Continuous Variables",
    notes = paste(
    "Panel A reports the mean (share equal to one) and number of",
    "observations for all binary variables used in the regression",
    "analysis; Panel B reports summary statistics for all continuous",
    "variables. Both panels are calculated over the final regression",
    "sample (N = 135; Table 2, Panel B). All continuous firm-level variables are",
    "winsorized at the 5th and 95th percentiles. The Diff (Central Asia",
    "$-$ Baltics) column reports the difference in means between the two",
    "regions and its statistical significance, based on a",
    "two-proportion z-test (Panel A) or a two-sample t-test (Panel B). A",
    "dash indicates the variable has no variation within at least one",
    "region, so no test statistic could be computed. All variables are",
    "defined in Appendix A. *, **, and *** denote statistical significance",
    "at the 10\\%, 5\\%, and 1\\% levels, respectively."
  )
), collapse = "\n"))
```

{{< pagebreak >}}

```{r}
#| results: asis

cat(paste(table_block(
  shrink(tab_country_panel_a),
  title = "Table 5: Descriptive Statistics by Country",
  subtitle = "Panel A: Binary Variables"
), collapse = "\n"))
```

```{r}
#| results: asis

cat(paste(table_block(
  shrink(tab_country_panel_b),
  title = "Panel B: Continuous Variables",
    notes = paste(
    "Panel A reports the mean (share equal to one) and number of",
    "observations for all binary variables used in the regression",
    "analysis, by country; Panel B reports the mean and standard",
    "deviation of the two continuous variables, by country. Both panels",
    "are calculated over the final regression sample (N = 135, Table 2, Panel B).",
    "All continuous firm-level variables are winsorized at the 5th and",
    "95th percentiles. All variables are defined in Appendix A."
  )
), collapse = "\n"))
```

{{< pagebreak >}}

```{r}
#| fig-width: 6
#| out-width: "100%"

fig_esg_disclosure + guides(fill = guide_legend(nrow = 2))
```

Fig. 2.—ESG Disclosure by Country. This figure classifies each sample firm by mandate status (mandated vs. not mandated) and ESG disclosure outcome (disclosed vs. not disclosed), and plots the percentage share of firms in each category, by country. The figure uses the full disclosure sample (N = 141) from Table 2, Panel A.

{{< pagebreak >}}

```{r}
#| results: asis

cat(paste(landscape_wrap(table_block(
  shrink(tab_corr),
  title = "Table 6: Pairwise Correlation Matrix",
    notes = paste(
    "This table reports pairwise Pearson correlation coefficients",
    "between the main variables used in the regression analysis,",
    "calculated over the final regression sample (N = 135). All variables",
    "are defined in Appendix A. *, **, and *** denote statistical",
    "significance at the 10\\%, 5\\%, and 1\\% levels, respectively."
  ),
  stretch = TRUE,
  width_cmd = "\\rotwidth"
)), collapse = "\n"))
```

```{r}
#| results: asis

cat(paste(table_block(
  shrink(tab_reg_main),
  title = "Table 7: Determinants of ESG Disclosure",
    notes = paste(
    "This table reports OLS (linear probability model) estimates of the",
    "determinants of ESG disclosure. The dependent variable,",
    "\\emph{ESG Disclosure}, equals one if a firm discloses ESG information either within its integrated annual report or in a standalone ESG report, and zero otherwise. Columns (1)--(4) report",
    "estimates from OLS regressions that include country fixed effects,",
    "which absorb all country-invariant characteristics and identify",
    "effects from within-country variation only. Columns (5)--(9) report",
    "pooled OLS estimates without country fixed effects, which instead",
    "include region and country-level institutional controls.",
    "For columns (1)--(4), Adj. R² (within) reports the share of",
    "within-country variation in \\emph{ESG Disclosure} explained by the",
    "covariates alone, net of the country fixed effects. Adj. R² (overall)",
    "reports the share of total variation explained by the covariates and",
    "fixed effects combined. Heteroskedasticity-robust (HC1) standard",
    "errors are reported in parentheses below each coefficient. All",
    "variables are defined in Appendix A. *, **, and *** denote statistical",
    "significance at the 10\\%, 5\\%, and 1\\% levels, respectively."
  )
), collapse = "\n"))
```

{{< pagebreak >}}

```{r}
#| results: asis

cat(paste(table_block(
  shrink(tab_reg_heterogeneity),
  title = "Table 8: Regional Heterogeneity in ESG Disclosure Determinants",
  center = TRUE,
    notes = paste(
    "This table examines whether the effect of foreign ownership, state ownership,",
    "mandatory ESG regulation, and Soviet-era incorporation on ESG",
    "disclosure differs by region. The dependent variable,",
    "\\emph{ESG Disclosure}, equals one if a firm discloses ESG information",
    "either within its integrated annual report or in a standalone ESG",
    "report, and zero otherwise. Each column reports a separate OLS regression with country fixed effects, including \\emph{Sensitive Industry}, \\emph{ln(Total Assets)}, and \\emph{ROA} as controls together with the indicated variable and its interaction with an indicator for Central Asia. Marginal",
    "Effect (Central Asia) reports the implied total effect of the",
    "variable of interest in Central Asian firms, computed as the sum of",
    "the base coefficient and the interaction coefficient; its standard",
    "error is computed via the delta method from the joint",
    "variance-covariance matrix of the two coefficients, and the",
    "associated 95\\% confidence interval is reported below.",
    "Heteroskedasticity-robust (HC1) standard errors are reported in",
    "parentheses below each coefficient. All variables are defined in",
    "Appendix A. *, **, and *** denote statistical significance at the",
    "10\\%, 5\\%, and 1\\% levels, respectively."
  )
), collapse = "\n"))
```

{{< pagebreak >}}

```{r}
#| results: asis

cat(paste(table_block(
  shrink(tab_reg_spillover),
  title = "Table 9: Regulatory Spillover in ESG Disclosure",
  center = TRUE,
    notes = paste(
    "This table presents a supplementary analysis of regulatory spillover",
    "in ESG disclosure, suggesting that non-mandated firms disclose more where an ESG mandate is already in",
    "force for other firms in their country. The dependent variable,",
    "\\emph{ESG Disclosure}, equals one if a firm discloses ESG information",
    "either within its integrated annual report or in a standalone ESG",
    "report, and zero otherwise. The sample is restricted to",
    "firms not themselves subject to a mandatory ESG disclosure",
    "requirement (N = 85). \\emph{Country ESG Mandate} equals one if a binding ESG disclosure mandate --- state or exchange-issued --- is in force for FY2024 in the firm's country, for at least part of its listed non-financial firm population, regardless of whether this specific firm is itself bound by it, and zero otherwise. Country fixed effects and region are not included: firms with no country-level mandate are located exclusively in Uzbekistan and Kyrgyzstan, so both would absorb most or all of this variable's variation. Heteroskedasticity-robust (HC1) standard errors",
    "are reported in parentheses below each coefficient. All variables",
    "are defined in Appendix A. *, **, and *** denote statistical significance",
    "at the 10\\%, 5\\%, and 1\\% levels, respectively."
  )
), collapse = "\n"))
```

{{< pagebreak >}}

```{r}
#| results: asis

cat(paste(longtable_block(
  shrink(tab_var_definitions),
  title = "Appendix A: Variable Definitions"
), collapse = "\n"))
```

{{< pagebreak >}}

```{r}
#| results: asis

cat(paste(table_block(
  shrink(tab_reg_robustness),
  title = "Appendix B: Firth Penalized Logistic Regression as Robustness Check",
  center = TRUE,
    notes = paste(
    "This table reports Firth's penalized maximum likelihood logistic",
    "regression estimates as a robustness check on the pooled",
    "specifications of Table 7, columns (5)--(9). The dependent variable is",
    "unchanged, \\emph{ESG Disclosure}. Column numbering corresponds to the",
    "matching specifications in Table 7. McFadden's",
    "pseudo-R-squared is reported in place of adjusted R-squared.",
    "Standard errors are reported in parentheses below each",
    "coefficient. All variables are defined in Appendix A. *, **, and ***",
    "denote statistical significance at the 10\\%, 5\\%, and 1\\% levels,",
    "respectively."
  )
), collapse = "\n"))
```

\pagebreak

# References {.unnumbered}

